Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-11 ms/main.tex
Another fix to result 3

Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
The assortment rate $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
Horizontal transmission is not always successful, as one partner may reject the other's phenotype. The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).

@@

\begin{corollary}[No assortment of transmission and cooperation]
Without assortment ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
(1) if the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; 
(2) if the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
\end{corollary}

@@

\begin{corollary}[Perfect assortment of transmission and cooperation]
With perfect assortment ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
\begin{equation}\label{eq:vert_hori_alpha1}
c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
\end{equation}
\end{corollary}
With perfect social association horizontal transmission always co-occurs with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}

>>>>

Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
Horizontal transmission is not always successful, as one partner may reject the other's phenotype. The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).

@@

\begin{corollary}[No social association of transmission and cooperation]
Without association ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
(1) if the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; 
(2) if the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
\end{corollary}

@@

\begin{corollary}[Perfect social association of transmission and cooperation]
With perfect social association ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
\begin{equation}\label{eq:vert_hori_alpha1}
c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
\end{equation}
\end{corollary}
With perfect social association horizontal transmission always co-occurs with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
\item \emph{Fixation of defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$; or 
	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_2$ and $c < \hat\gamma_1$; or
  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}
